EvoSwarm: A Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-05-18 draft.tex
Still one question to go

In this paper, we have presented the EvoSwarm framework for 
the reproducible execution of experiments with an event-based, cloud-native architecture 
suitable for hosting multi-population, multi-algorithm optimization algorithms. % reproducible? It's in the title - JJ Yes - M
The framework is based in industry-standard development
tools such as Docker and Docker Compose, making it easy for scientists and practitioners to develop and deploy
multi-algorithm distributed experiments. The model is based on the asynchronous
exchange of messages between stateless functions that react to a continuous
stream of data. We show the differences of the message-driven architecture we presented against
four other proposals for multi-population algorithms found in the literature, and highlight the 
advantages for conducting asynchronous multi-population algorithms.
% But it's not a practical comparison, but a theoretical one. Show the differences instead of compare? - JJ - Ok 
% We found that it is best suited for asynchronous multi-population algorithms. % This is not really proved. You chose, you didn't find - JJ
% Ok, I put it in the same package - M

We proposed a new methodology for the reproducible deployment and execution of
multiple experiments by specifying the infrastructure as part of an experiment
definition in both local or cloud environments. We presented the workflow of an
experiment's entire life-cycle viewed from the perspective of developers and
researchers.  % and we proved... Remember the experimental hypothesis - JJ - Ok - 
We tested the deployment of an experiment on Amazon's Elastic
Container Service, and proved that as cloud-native, container-based application,
EvoSwarm could be deployed locally or in the cloud by specifying the configuration 
of container images and resources in an orchestration service.

@@

A second experiment centered on evaluating the algorithmic benefits (experiments
taking less time because they need fewer evaluations) of distributed
multi-algorithm algorithms. We compared the homogeneous and an ensemble of
multi-populations, using Genetic Algorithms (GAs) and Particle Swarm
Optimization (PSO) using the COCO benchmark framework 
for visualization and definition of the optimization problems. % as a visualization device? - JJ  
% we also used their functions -M
We found that the set-up of these algorithms has a significant influence on
their results since diversity is essential for their performance. The ensemble
achieved better results and, in most cases, needed fewer evaluations.

>>>>

In this paper we have presented the EvoSwarm framework for 
the reproducible execution of experiments with an event-based, cloud-native architecture 
suitable for hosting multi-population, multi-algorithm optimization
methods. % Too many algorithms, there's no such thing as a
         % multi-algorithm algorithm - JJ
The framework is based in industry-standard development
tools such as Docker and Docker Compose, making it easy for scientists and practitioners to develop and deploy
multi-algorithm distributed experiments. The model implemented by the
framework is based on the asynchronous % Please distinguish model,
                                % framework, implementation, algorithm
                                % - JJ
exchange of messages between stateless functions that react to a continuous
stream of data; populations are the messages that flow in this stream. We show the differences of the message-driven architecture we presented against
four other proposals for multi-population algorithms found in the literature, and highlight the 
advantages for conducting asynchronous multi-population algorithms.

We proposed a new methodology for the reproducible deployment and execution of
multiple experiments by specifying the infrastructure as part of an experiment
definition in both local and cloud environments. We presented the workflow of an
experiment's entire life-cycle viewed from the perspective of developers and
researchers. 
We tested the deployment of an experiment on Amazon's Elastic
Container Service, and proved that as a cloud-native, container-based application,
EvoSwarm could be deployed locally or in the cloud by specifying the configuration 
of container images and resources in an orchestration service.

@@

A second experiment centered on evaluating the algorithmic benefits (experiments
taking less time because they need fewer evaluations) of distributed
multi-algorithm algorithms. We compared the homogeneous and an ensemble of
multi-populations, using Genetic Algorithms (GAs) and Particle Swarm
Optimization (PSO) using the COCO benchmark framework 
for visualization and definition of the optimization problems.
We found that the set-up of these algorithms has a significant influence on
their results since diversity is essential for their performance. The ensemble
achieved better results and, in most cases, needed fewer evaluations.
